Apropos Replacement \newline (Initial Outline)

### 2011-12-26 paper.tex
Clarify

\documentclass[titlepage, a4paper, 12pt]{article}
\usepackage{listings}
\usepackage{color}
\usepackage[pdftex]{graphicx}
\usepackage{graphicx}
\usepackage[colorlinks=false]{hyperref}
\lstset{ %
language=sh,
basicstyle=\footnotesize,
numbers=none,
backgroundcolor=\color{white},
showspaces=false,
showstringspaces=false,
showtabs=false,
frame=single,
tabsize=2,
captionpos=b,
breaklines=true,
breakatwhitespace=false,
title=\lstname
}
\title{Apropos Replacement \newline
(Extended  Abstract)}
\author{Abhinav Upadhyay $<$er.abhinav.upadhyay@gmail.com$>$ \and 
Joerg Sonnenberger $<$joerg@NetBSD.org$>$}
\begin{document}
\maketitle
\section{Abstract}
Unix like operating systems have withstood the test of time for 40 odd years for
several technical and philosophical reasons. One of those reasons is the
quality documentation they ship in the form of man pages. They are a single point
source of consultation for most of our routine work. But there has been a lack of
good search tool to accompany this documentation which would increase their
usefulness manifolds.

Traditionally \textit{apropos} [1] has been there to act as a search
interface but to a large extent it hasn't really lived up to it's expectation.
\textit{apropos} was
developed in the early days of Unix when computing resources were scarce and
which was the primary reason that it's design was kept so
minimal and simple.

In this paper the limitations of the traditional implementation of
\textit{apropos} are discussed along with brief details of how those limitations
were solved in this implementation and also what other modern implementations
are available out there.
\section{Introduction}
The classical version of \textit{apropos} has been implemented by simply
indexing the keywords in the NAME section of the man pages in a plain text file
(whatis.db) [2]
and performing searches on it. The reason for this simple design was most
probably lack of computing resources in the early days. The plain text file
consisting of keywords would hardly take few hundreds of kilo bytes of disk space
and performing search on a plain text file is also not very hard.

>>>>

\documentclass[titlepage, a4paper, 12pt]{article}
\usepackage{listings}
\usepackage{color}
\usepackage[pdftex]{graphicx}
\usepackage{graphicx}
\usepackage[colorlinks=false]{hyperref}
\lstset{ %
language=sh,
basicstyle=\footnotesize,
numbers=none,
backgroundcolor=\color{white},
showspaces=false,
showstringspaces=false,
showtabs=false,
frame=single,
tabsize=2,
captionpos=b,
breaklines=true,
breakatwhitespace=false,
title=\lstname
}
\title{Apropos Replacement \newline
(Initial Outline)}
\author{Abhinav Upadhyay $<$er.abhinav.upadhyay@gmail.com$>$ \and 
Joerg Sonnenberger $<$joerg@NetBSD.org$>$}
\begin{document}
\maketitle
\section{Abstract}
Unix like operating systems have withstood the test of time for 40 odd years for
several technical and philosophical reasons. One of those reasons is the
quality documentation they ship in the form of man pages. They are a single point
source of consultation for most of our routine work. But there has been a lack of
good search tool to accompany this documentation which would increase their
usefulness manifolds.

Traditionally \textit{apropos} [1] has been there to act as a search
interface but to a large extent it hasn't really lived up to it's expectation.
\textit{apropos} was
developed in the early days of Unix when computing resources were scarce and
which is the primary reason that it's design was kept so
minimal and simple.

In this paper the limitations of the traditional implementation of
\textit{apropos} are discussed along with brief details of how those limitations
have been solved in the implementation developed as part of this project and also
what other modern implementations are available out there.
\section{Introduction}
The classical version of \textit{apropos} has been implemented by simply
indexing the keywords in the NAME section of the man pages in a plain text file
(whatis.db) [2]
and performing searches on it. The reason for this simple design was most
probably lack of computing resources in the early days. The plain text file
consisting of keywords would hardly take few hundreds of kilo bytes of disk space
and performing search on a plain text file is also not very hard.
